\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,            % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\usepackage{changepage}
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Adam Amin}

\vspace{5pt}

% contact information
\centerline{\href{mailto:adamamin54@gmail.com}{adamamin54@gmail.com} | \textnormal{tel: +61 438 627 158}} 
% \vspace{0.1cm}

% summary section
\begin{adjustwidth}{2cm}{2cm}
  \begin{center}
    \textit{\small{Recent Computer Engineering B.S. graduate with passions in electronics and software design, seeking an entry-level role in embedded systems or software development.}}
  \end{center}
\end{adjustwidth}
\vspace{-0.2cm}

% skills section
%% software engineering skills
\section*{Software Engineering Skills}
\textbf{Programming Languages:} C, C++, C\#, GoLang, Java, JavaScript, HTML5/CSS, Python \\
\textbf{Technologies and Protocols:} Docker, Embedded Linux, Git, GCC/GDB, Gitlab CI/CD, Yocto Project \\
\textbf{Frameworks:} Selenium, React, Django, Robot
\vspace{-11.5pt}

%% Embedded Systems skills - electrical engineering
\section*{Electrical Engineering Skills}
\textbf{Programming Languages:} ARM Assembly, MIPS Assembly, Verilog \\
\textbf{Technologies and Protocols:} Arduino, FreeRTOS, SPI, UART, VDHL \\
\textbf{Simulation Tools:} MATLAB, OrCAD, PSpice, Synopsis \\
\vspace{-8.5pt}

% education section
\section*{Education/Certifications}
\textbf{University of California, Riverside} -- Bachelors of Science in Computer Engineering \hfill December 2024 \\
\textbf{Irvine Valley College} -- Associates in Computer Science and Mathematics \hfill June 2022 \\
\textbf{NCEES Fundamentals of Engineering} -- Electrical and Computer Engineering Certification \hfill \textbf{In Progress}

\vspace{-8.5pt}

% experience section
\section*{Experience}
\textbf{Quality Assurance Engineer,} {Promenade Software} -- Irvine, CA \hfill June 2020 -- August 2022 \\
\vspace{-9pt}
\begin{itemize}
  % STAR: situation
  \item Worked on the DxTerity COVID Project, a high-priority initiative to develop a web-based solution for purchasing test kits and securely storing COVID-19 related data.
  % STAR: task
  \item Ensured software quality by designing and executing test cases, identifying and reporting bugs, and verifying fixes.
  % STAR: action
  \item Maintained detailed documentation of performed test cases, test validation, and test verification.
  % STAR: result
  \item Contributed to the successful delivery of a scalable, reliable, and secure system that met client requirements.
\end{itemize}

\textbf{Software Developer,} {Planet Innovation} -- Melbourne, AU\hfill July 2025 -- \textit{Current} \\
\vspace{-9pt}
\begin{itemize}
  % STAR: situation
  \item Worked on Project Archimedes, involved software implementation and maintenance of an embedded Linux system for several manufactured peristaltic pumps.
  % STAR: task
  \item Utilized Yocto Project to build lightweight embedded Linux images and Python for integration across several applications in the software system.
  \item Facilitated software development using Docker containers, virtual environments, and Gitlab CI/CD.
  % STAR: action
  \item Developed automated test suites in Python and Robot Framework, increased test coverage and reduced manual QA efforts.
  % STAR: result
  \item Assisted in debugging and resolving system-level issues in production units, ensuring reliability of the pumps and improving client relations.
\end{itemize}
% \textbf{Job Title,} \href{https://www.fstl1992.com/}{Company} -- City, ST \hfill XXXX -- XXXX \\
% \vspace{-9pt}

\vspace{-18.5pt}

% projects section
\section*{Projects}

\textbf{Synthesizer - FRDM K64F Microcontroller} %\hfill \href{https://www.hardwareishard.net/portfolio-database}{blog.com/projectname} \\
\vspace{-7pt}
\begin{itemize}
  \item Built a digital synthesizer using the FRDM-K64F microcontroller by implementing signal processing algorithms in C.
  \item Designed the circuit and hardware which allowed to user to adjust volume and add effects to the audio signal.
  \item Utilized ARM Cortex-M4 capabilities for real-time audio synthesis and debugging with GDB. 
\end{itemize}

\textbf{Volumetric Display Visualizer - Raspberry Pi Pico 2} %\hfill \href{https://mitcommlab.mit.edu/meche/commkit/portfolio/}{\textbf{In Progress}} \\
\vspace{-7pt}
\begin{itemize}
  \item Designed a 3D visualizer using a Raspberry Pi 5 to display real-time images and video.
  \item Integrated the system with TouchDesigner, an app for live visualization and user interaction.
  \item Currently iterating on the design to improve performance and functionality.
\end{itemize}

% alternate formatting for projects section
% \section*{Projects}
% \begin{itemize}
%   \item \textbf{QuantSoftware Toolkit:} Open source Python library for data analysis and machine learning for finance
%   \item \textbf{GitHub Visualization:} Data visualization of Git Log data using D3 to analyze project trends over time
%   \item \textbf{Recommendation System:} Music and movie recommender systems using collaborative filtering on public datasets
%   \item \textbf{Mac Setup:} Book that gives step by step instructions on setting up developer environment on Mac OS
% \end{itemize}


\end{document}
